Data preparation for employee category analysis

### 2023-06-13 04. Analysis/scripts/02_data_preparation_clusters_employee.Rmd
Update 02_data_preparation_clusters_employee.Rmd
Attempting to update this with new variables
Update 02_data_preparation_clusters_employee.Rmd
Added to day of week counts telework and counts and proportion report to the job site, indicator for exiting employment, and count of unique supervisors, and indicator for multiple supervisors

#### Proportion of days remote by day of the week

@@

```{r}
prep_xx <- 
  prep_day_of_week %>% 
  select(person_id,date_day_of_week,daily_status_teleworking_working_prop,daily_status_teleworking_observation_prop) %>% 
  pivot_longer(cols = starts_with("daily_status")) %>% 
  mutate(date_day_of_week = str_to_lower(date_day_of_week)) %>% 
  unite("name",date_day_of_week,name) %>% 
  pivot_wider(values_from = value, names_from = name) %>% 
  mutate(
    across(
      .cols = where(is.numeric),
      .fns = ~replace_na(.,0)
    )
  )
```

@@

>>>>

#### Proportion of days remote or reporting to site by day of the week

@@

```{r}
prep_xx <- 
  prep_day_of_week %>% 
  select(person_id,date_day_of_week,
         daily_status_teleworking,
         daily_status_teleworking_working_prop,
         daily_status_teleworking_observation_prop,
         daily_status_reporting_to_job_site,
         daily_status_reporting_to_job_site_working_prop,
         daily_status_reporting_to_job_site_observation_prop) %>% 
  pivot_longer(cols = starts_with("daily_status")) %>% 
  mutate(date_day_of_week = str_to_lower(date_day_of_week)) %>% 
  unite("name",date_day_of_week,name) %>% 
  pivot_wider(values_from = value, names_from = name) %>% 
  mutate(
    across(
      .cols = where(is.numeric),
      .fns = ~replace_na(.,0)
    )
  )
```

@@

### Exit employment

Identify employees who had a report date earlier than the last reporting day.

```{r}
prep_a <-
  cohort_panel %>% 
  select(person_id,date,daily_status_imputed) %>% 
  arrange(person_id,date) %>% 
  group_by(person_id) %>% 
  summarise(
    across(
      .cols = c(date,daily_status_imputed),
      .fns = last
    )
  ) %>% 
  ungroup() %>%
  mutate(
    exit_employment = case_when(date < max(date) ~ 1,
                                TRUE ~ 0)
  ) %>% 
  distinct()
```

Review grouping by `daily_status_imputed`.

```{r}
prep_a %>% 
  group_by(daily_status_imputed) %>% 
  skim()
```

Remove `daily_status_imputed`.

```{r}
prep_xx <- 
  prep_a %>% 
  select(-daily_status_imputed)
```

### Number of supervisors

Count number of unique supervisors per employee.

```{r}
prep_xx <-
  cohort_panel %>% 
  select(person_id,supervisor_e_mail_address) %>% 
  group_by(person_id) %>% 
  summarise(
    across(
      .cols = c(supervisor_e_mail_address),
      .fns = c(n_distinct = n_distinct),
      .names = "{.col}_{.fn}"
    )
  ) %>% 
  ungroup() %>%
  mutate(
    multiple_supervisors = case_when(supervisor_e_mail_address_n_distinct > 1 ~ 1,
                                     supervisor_e_mail_address_n_distinct == 1 ~ 0,
                                TRUE ~ 0)
  ) %>% 
  distinct()
```
